cardinalR: Generating Interesting High-Dimensional Data Structures

### 2025-12-11 paper-cardinalR.Rmd
Added scripts
Fixed the clustering figure

```{r layouts}

@@

```{r}
error_five_clust <- read_rds("data/five_clusts/five_clusts_hbe.rds")

@@

```{r fig-cluster-stats, fig.width=10, fig.height=3, out.width="100%", layout="l-body"}
# Examine the cluster stats
all_stats <- bind_rows(hc_stats, kmeans_stats)
all_stats |>
  pivot_longer(within.cluster.ss:sindex, names_to = "stat", values_to = "value") |>
  ggplot(aes(x=cl, y=value, colour=method)) +
    geom_line() +
    facet_wrap(~stat, ncol=3, scales="free_y") +
    xlab("Number of clusters") +
    ylab("")
```

>>>>

<!--scripts/five_clusts/02_gen_embeddings.R-->
```{r layouts}

@@

<!--scripts/five_clusts/03_gen_rmse.R-->
```{r}
error_five_clust <- read_rds("data/five_clusts/five_clusts_hbe.rds")

@@

```{r fig-cluster-stats, fig.width=10, fig.height=3, out.width="100%", layout="l-body"}
# Examine the cluster stats
all_stats <- bind_rows(hc_stats, kmeans_stats)
all_stats |>
  pivot_longer(within.cluster.ss:sindex, names_to = "stat", values_to = "value") |>
  ggplot(aes(x=cl, y=value, colour=method)) +
    geom_line() +
    facet_wrap(~stat, ncol=3, scales="free_y") +
    xlab("Number of clusters") +
    ylab("") +
    theme_minimal() +
    theme(panel.border = element_rect(fill = 'transparent'),
          plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
          axis.ticks.x = element_line(),
          axis.ticks.y = element_line(),
          legend.position = "none",
          axis.text.x = element_text(size = 7),
          axis.text.y = element_text(size = 7),
          axis.title.x = element_text(size = 7),
          axis.title.y = element_text(size = 7),
          plot.margin = margin(0, 0, 0, 0))
```
